---
title       : Data Product Regression
subtitle    : 
author      : The Clown Bongo
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

---

## Regression Model Derived

The file DevDataProdRegData should be in your working directory. The file has information about the log return of the S&P 500 and GE for the period 2004 to 2014.  
With the provided data, we will find whether the correlation coefficient indicates there seems to be a linear relationship between the log return of GE and S&P 500. We will derive a linear regression model of GE against the S&P 500, plot the data against the regression line, and a scatter plot of the residuals versus the predicted values.
```{r read_data, echo = FALSE}
data_stock <- read.csv('DevDataProdRegData.csv', header = TRUE, sep = ",")
sumdata_stock <- summary(data_stock)
#print(sumdata_stock)
correlation_GESP500_pearson <- cor(data_stock$lnadjcloseGE, data_stock$lnadjcloseSP500, method = "pearson")
#print(correlation_GESP500_pearson)
lmfitGEvsSP500 <- lm(data_stock$lnadjcloseGE ~ data_stock$lnadjcloseSP500)
sum_lmfitGEvsSP500 <- summary(lmfitGEvsSP500)
print(lmfitGEvsSP500)
```

---

## Scatter Plot Data with Regression Line

```{r ScatterPlot, echo = FALSE}
require(ggplot2)
scatterGESP500 <- ggplot(data_stock, aes(lnadjcloseSP500, lnadjcloseGE)) + 
    geom_point(colour = "red") + 
    ggtitle("Scatterplot Log Return GE vs Log ReturnS&P 500") + 
    xlab("Log Return S&P 500") + 
    ylab("Log Return GE") + 
    geom_smooth(method=lm, se=FALSE)
print(scatterGESP500)
```

---

## Scatter Plot of the residuals against fitted values

```{r ScatterResidualvsFitted, echo = FALSE}
# Predict the values
data_pred <- predict(lmfitGEvsSP500)

# Get the residuals
residuals <- data_stock$lnadjcloseGE - data_pred
data_predres <- data.frame(residuals, data_pred)

# Plot the residuals against fitted data
scatterresidualsvspredicted <- ggplot(data_predres, aes(residuals, data_pred)) + 
    geom_point(colour = "red") + 
    ggtitle("Scatterplot Residuals vs Predicted") + 
    xlab("Predicted") + 
    ylab("Residuals") 
print(scatterresidualsvspredicted)
```

---

## Should we revisit the model?

Yes as from the Shapiro tests, we find the data is not normally distributed since the p-Value are extremely small.
```{r justificationGE, echo = FALSE}
print(shapiro.test(data_stock$lnadjcloseGE)) 
print(shapiro.test(data_stock$lnadjcloseSP500))
```
